---
title: "Assignment 2"
---

# Assignment 2

```{r}
library(rvest)
library(tidyverse)
library(stringr) 
library(ggplot2)
url1 <- "https://www.imdb.com/search/title/?title_type=feature&release_date=2010-01-01,2023-12-31&num_votes=2500,&country_of_origin=TR&count=250"
url2 <- "https://www.imdb.com/search/title/?title_type=feature&release_date=,2009-12-31&num_votes=2500,&country_of_origin=TR&count=250"
urls <-c(url1,url2)
data_html <- read_html(url1)
data_html <- read_html(url2)


#films <- tab |> setNames(c("Title", "Year", "Duration","Rating", "Votes")) 
title_names <- data_html |> html_nodes('.ipc-title__text')
title_names <- html_text(title_names)
title_names <- tail(head(title_names,-1),-1)
title_names <- str_split(title_names, " ", n=2)
title_names <- unlist(lapply(title_names, function(x) {x[2]}))

year <- data_html |> html_nodes('.sc-43986a27-8.jHYIIK.dli-title-metadata-item:nth-child(1)')
year <- html_text(year)
year <- tail(head(year,-1),-1)
year <- unlist(lapply(year, function(x) {x[2]}))
year <- as.numeric(year)

duration <- data_html |> html_nodes('.sc-43986a27-8.jHYIIK.dli-title-metadata-item:nth-child(2)')
duration <- html_text(duration)
hour <- as.numeric(str_extract(duration, "\\d+(?=h)"))
replace_na(hour, 0)
minute <- as.numeric(str_extract(duration, "\\d+(?=m)"))
replace_na(minute, 0)
duration <- 60 * hour + minute


rating <- data_html |> html_nodes('.ratingGroup--imdb-rating')
rating <- html_text(rating)
rating <- str_extract(rating, "\\d+\\.\\d+") 
rating <- as.numeric(rating)

votes <- data_html |> html_nodes('.sc-53c98e73-0.kRnqtn')
votes <- html_text(votes)
pattern <- "[^0-9]"
votes <- as.numeric(str_subset(votes, pattern))
```
3.a) Top 5 are Ye??il??am films like "Hababam S??n??f??", "Tosun Pa??a", "S??t Karde??ler" and "CM101MMXI Fundamentals".These classics resonate with me through their timeless humor, well-crafted narratives, and unforgettable characters, earning them a special place in my heart.I love comedy, but Kemal Sunal holds a special place in my heart in this genre. So, I wasn't surprised to see his films in the top 5.
```{r}
arrange(desc(rating)) %>%
  slice_max(rating, n = 5)
arrange(desc(rating)) %>%
  slice_min(rating, n= 5)
```
3.b) I choose CM101MMXI Fundamentals and Hababam S??n??f?? from my favorites and they both have high rates. I think people loves comedy like me.
```{r}
select(title_names = c("CM101MMXI Fundamentals","Hababam S??n??f??"))
```


group_by((year))%>%
summarise(average_rating = mean(rating))%>%
ggplot(aes(year, average_rating))+
  geom_point()

number_of_movies <- count(title_names)%>%
  ggplot(aes(year , number_of_movies)) +
  geom_point()

number_of_movies <- count(title_names)%>%
  ggplot(aes(year , number_of_movies)) +
  geom_boxplot()

group_by((year))%>%
ggplot(aes(rating, votes))+
  geom_point()

group_by((year))%>%
ggplot(aes(rating, duration))+
  geom_point()

arrange(desc(rating)) %>%
  top_n(1000)
```
